Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2023-03-04 paper/discussion.tex
added Supplement S1
Related works
Examine solutions

As shown, the need for computation time increases with the power of two with the resolution. 
Similarly, the usage of main memory increases. 
Which in tern limits the processable data points and resolution.
On the error only scales linear with the resolution. 
Hence, there is a diminishing return of smaller errors, compared to compute time and resources used.

Therefore, this worked tries a) to reduce the needed compute power and b) decrease the deviation for a given resolution.

For b), two methods have been used to increase the similarity of the paths computed from medium resolution raster, to the path of the highest resolution raster.
These methods can be used as surrogates for the more complex calculation of the least cost path with the higher resolution.
In the first method a bi-linear down sampling of the higher resolution raster has been applied and in the second method, the all touched false and true raster where averaged in different ratios, to computed the optimum mixed raster, for the used costs.
While the second method of using an averaged raster, a higher similarity to the path from the highest resolution raster, the down sampling method is more
simple and does not need to be optimized for the given costs.
Hence, it is easier and widely applicable.

@@

As the original least cost path QGIS plug-in the used algorithm stops the least aggregation of the costs after the final end point has been found.
This early stopping might result in sub-optimal paths around the end points for some edge cases, where the connection via another neighbor might be more optimal.

The set of rules that are used create the cost raster, includes a rule for creating a buffer around buildings  which is set to the level \textbf{prohibited} areas.
While the used data set for buildings, also includes power poles, the area of the level \textbf{preferential} power grid, includes isles of high costs. 
In further works, these should be excluded.

In this work, the effect of computation costs and deviation of the results, is examined for a very limited set of points.
Also, only the costs of finding the least cost path from one starting point, to a single end point has been considered.
When, multiple endpoints are used, the computation cost for the aggregated cost raster has only to computed once.
On the other hand the effect early stopping is not as dramatic, because the algorithm would only stop early for the last end point with the highest cost.
When calculating several paths from one raster, the benefits of chapter~\ref{subsec:faster-processing-of-the-cost-path-algorithm} is reduced.
Especially, the pre-calculation on lower resolution raster and buffering of the resulting paths as a restricted search area decreases in it effectivity.
As the number of paths rises, fewer of points in higher resolution cost raster will be deselected for the final estimation of the least cost path.

In this work, the single cost raster layers aggregated with the maximum function. 
Another possible aggregation function is the sum.
Each aggregation function can be justified, by a different interpretation of the costs and its scale.
The reasoning of selection the maximum function is, limiting the maximum costs.
When the \textbf{prohibited} level is used as the highest level.
Than higher levels are prohibited within the concept.
This an area even more prohibited, when it is included in two different rules of the level?
On the other side, This aggregation is unable to differentiate between these nuances, as  the sum function is.
This way, one can differential between, different sub-levels.
One consequence is, that a small mediation between high and low single cost raster, in the final cost raster is possible.

>>>>

% !TeX spellcheck = en_US
As shown, the need for computation time increases with the power of two with the resolution. 
Similarly, the usage of main memory increases. 
Which in tern limits the processable data points and resolution.
On the error only scales linear with the resolution. 
Hence, there is a diminishing return of smaller errors, compared to compute time and resources used.

Therefore, this worked tries a) to reduce the needed to compute power and b) decrease the deviation for a given resolution.

For b), two methods have been used to increase the similarity of the paths computed from medium resolution raster, to the path of the highest resolution raster.
These methods can be used as surrogates for the more complex calculation of the least cost path with the higher resolution.
In the first method a bi-linear down sampling of the higher resolution raster has been applied and in the second method, the all touched false and true raster where averaged in different ratios, to compute the optimum mixed raster, for the used costs.
While the second method of using an averaged raster, a higher similarity to the path from the highest resolution raster, the down sampling method is more
simple and does not need to be optimized for the given costs.
Hence, it is easier and widely applicable.

@@

As the original least cost path QGIS plug-in the used algorithm stops the least aggregation of the costs after the final end point has been found.
This early stopping might result in suboptimal paths around the end points for some edge cases, where the connection via another neighbor might be more optimal.

The set of rules that are used create the cost raster, includes a rule for creating a buffer around buildings  which is set to the level \textit{prohibited} areas.
The resolution of the medium level raster needs to be high enough to crudely show every detail, Hence at least in the magnitude of the minimum object size plus twice its buffer, in this example in the range of at least 25~m or 10~m.
Although the overall result can change, due super position of objects and there buffer.
Nevertheless, does higher resolution resemble, the geography more precise, but in addition show paths that are too small, to be taken.
On the other hand, as the run from the starting point to the end point at a resolution of 2.5~m shows, new ways, that could not not be reached before, do hint inconsistencies of the rules that construct the cost raster.

Object and there buffer might leave a  path that, is smaller than 10~m resolution.
So a second rule to find a good resolution, that is should be in the magnitude of the size of the structure  to be build.
While the used data set for buildings, also includes power poles, the area of the level \textit{preferential} power grid, includes isles of high costs. 
In further works, these should be excluded.

In this work, the effect of computation costs and deviation of the results, is examined for a very limited set of points.
Also, only the costs of finding the least cost path from one starting point, to a single end point has been considered.
When, multiple endpoints are used, the computation cost for the aggregated cost raster has only to computed once.
On the other hand the effect early stopping is not as dramatic, because the algorithm would only stop early for the last end point with the highest cost.
When calculating several paths from one raster, the benefits of chapter~\ref{subsec:faster-processing-of-the-cost-path-algorithm} is reduced.
Especially, the pre-calculation on lower resolution raster and buffering of the resulting paths as a restricted search area decreases in its effectivity.
As the number of paths rises, fewer of points in higher resolution cost raster will be deselected for the final estimation of the least cost path.
The least cost algorithm does only select the most cost-effective path.
Therefore, paths of similar, but slightly worse cost are stay unknown.
An end-user might be interested in selecting a path from a set of possible paths of similar aggregated costs and apply an adapted set evaluation criteria.
This can be achieved a by adapting the backtracking, to get an array of paths or by applying perturbation on the costs.

In this work, the single cost raster layers aggregated with the maximum function. 
Another possible aggregation function is the sum.
Each aggregation function can be justified, by a different interpretation of the costs and its scale.
The reasoning of selection the maximum function is, limiting the maximum costs.
When the \textit{prohibited} level is used as the highest level.
Then higher levels are \textit{prohibited} within the concept.
This an area even more \textit{prohibited}, when it is included in two different rules of the level?
On the other side, This aggregation is unable to differentiate between these nuances, as  the sum function is.
This way, one can differential between, different sublevels.
One consequence is, that a small mediation between high and low single cost raster, in the final cost raster is possible.

### 2023-03-04 paper/methods.tex
added Supplement S1
Related works
Examine solutions

The nationwide land coverage (ATKIS) with a scale of 1:250000 are provided by the Federal Agency for Cartography
and Geodesy~\cite{noauthor_digitales_2021}.
The nationwide power grid (tags: 'power': line) has been retrieved via OpenStreetMap~\cite{boeing_osmnx_2017}.
Local data as houses at Level of Detail 1 are offered by the State Office for Geoinformation and Land Surveying of
Lower Saxony\cite{noauthor_opengeodatani_2022}.
In addition, local planning geodata for the land usage are taken
from 'Metropolplaner' (Planing data Lower Saxony \& Bremen)\cite{noauthor_metropolplaner_2022}

PyWPS\cite{noauthor_welcome_2016} is used to offer the least cost path algorithm as a \acrfull{wps}.
The initial implementation of the least cost path algorithm is based on the implementation for the QGIS-Plugin
'Least Cost Path'\cite{noauthor_leastcostpathdijkstra_algorithmpy_2022} in version 1.0.

The different layers from the different entities are optionally filtered, buffered and then rasterized.
Filtering the layers of the files for special attributes enables to further differentiate.
For examples makes it possible to differentiate between heath and uncultivated land.
Adding a buffer can be used either used to convert a line objects as power grids and streets into a polygon with the
correct physical width, or to add minimum distance from an existing of planed area to the new power grid.
Each of theses rasterized layers are given a weight, or cost that expresses the cost of using land covered by this layer.
The costs of all layers of is aggregated with the maximum function.
Thus, an area covered by multiple layers is uniformly used with the highest costs.
For every area in the study area, that is not covered by any layer, is given the default cost.
The costs have been grouped into different levels~(see table~\ref{tab:1}) starting from preferential areas with
very low costs, via no restrictions, which is the default, used when no other layers are covering the local area,
to restricted, strongly restricted and prohibited areas with high costs.
These higher costs resemble the degree how much a local area should be avoided, while routing the path.
The ratio of the higher costs to the lower costs directly translates into the additional diversion in pixels
the algorithm is willing to go, for avoiding an area of high costs.
Thus, as prohibited areas describe a legal obligation, not to use these areas or only to the utmost minimum,
the weight that resembles the costs for these types of areas, has to be especially high. \\
The rasterization transforms a vector into a raster.
The rasterization can be executed in to different ways.
In both ways, the rasterization can be imaged, as the old vector is layered over the new raster grid with the new
given resolution and the new affine transformation and the coordinate reference system of the vector.
Both rasterization techniques differ in how the pixels are selected, that describe, that a geo-object overlays the pixel.
The pixels can either be described as overlaid with a geo-object, when either the center of that pixel is overlaid
by the geo-object, or any part of the pixel is overlaid.
Hence, the version with any part overlaid is called all touched True.
The version where a overlaid pixel center is require is thus called all touched False.
All touched False is considered the default (see figure~\ref{fig:alltouched}).
\begin{figure}[!ht]
	\centering

@@

The whole stack of the cost raster, via the aggregated costs to the resulting least cost path can is shown with an example for a starting cost raster of 50~m resolution and a rasterization with all touched False (see \ref{fig:costs2path}).
Because of the early stopping strategy used in the aggregation sub-paths with high costs have not been fully computed.
Instead, the execution stops early after reaching the end point.
Because the end point ends at a power transformer, which is a building type, the paths ends at in a Prohibited Area.
Therefore, areas even farther away from the starting point have been explored first.

>>>>

The nationwide land coverage (ATKIS) with a scale of 1:250000 are provided by the Federal Agency for Cartography
and Geodesy~\cite{noauthor_digitales_2021}.
The nationwide power grid (tags: 'power': line) has been retrieved via OpenStreetMap~\cite{boeing_osmnx_2017}.
Local data as houses at Level of Detail 1 are offered by the State Office for Geoinformation and Land Surveying of
Lower Saxony~\cite{noauthor_opengeodatani_2022}.
In addition, local planning geodata for the land usage are taken
from 'Metropolplaner' (Planing data Lower Saxony \& Bremen)~\cite{noauthor_metropolplaner_2022}.

PyWPS~\cite{noauthor_welcome_2016} is used to offer the least cost path algorithm as a \acrfull{wps}.
The initial implementation of the least cost path algorithm is based on the implementation for the QGIS-Plugin
'Least Cost Path'~\cite{noauthor_leastcostpathdijkstra_algorithmpy_2022} in version 1.0.

The different layers from the different entities are optionally filtered, buffered and then rasterized.
Filtering the layers of the files for special attributes enables to further differentiate.
For examples makes it possible to differentiate between heath and uncultivated land.
Adding a buffer can be used either used to convert a line objects as power grids and streets into a polygon with the
correct physical width, or to add minimum distance from an existing of planed area to the new power grid.
Each of theses rasterized layers are given a weight, or cost that expresses the cost of using land covered by this layer.
The costs of all layers of is aggregated with the maximum function.
Thus, an area covered by multiple layers is uniformly used with the highest costs.
For every area in the study area, that is not covered by any layer, is given the default cost.
The costs have been grouped into different levels~(see table~\ref{tab:1}) starting from \textit{preferential} areas with
very low costs, via \textit{no restriction}s, which is the default, used when no other layers are covering the local area,
to \textit{restricted}, \textit{strongly restricted} and \textit{prohibited} areas with high costs.
These higher costs resemble the degree how much a local area should be avoided, while routing the path.
The ratio of the higher costs to the lower costs directly translates into the additional diversion in pixels
the algorithm is willing to go, for avoiding an area of high costs.
Thus, as \textit{prohibited} areas describe a legal obligation, not to use these areas or only to the utmost minimum,
the weight that resembles the costs for these types of areas, has to be especially high. \\
The rasterization transforms a vector into a raster.
The rasterization can be executed in to different ways.
In both ways, the rasterization can be imaged, as the old vector is layered over the new raster grid with the new
given resolution and the new affine transformation and the coordinate reference system of the vector.
Both rasterization techniques differ in how the pixels are selected, that describe, that a geo-object overlays the pixel.
The pixels can either be described as overlaid with a geo-object, when either the center of that pixel is overlaid
by the geo-object, or any part of the pixel is overlaid.
Hence, the version with any part overlaid is called all touched True.
The version where a overlaid pixel center is require is thus called all touched False.
All touched False is considered the default (see figure~\ref{fig:alltouched}).
\begin{figure}[!ht]
	\centering

@@

The whole stack of the cost raster, via the aggregated costs to the resulting least cost path can is shown with an example for a starting cost raster of 50~m resolution and a rasterization with all touched False (see \ref{fig:costs2path}).
Because of the early stopping strategy used in the aggregation sub-paths with high costs have not been fully computed.
Instead, the execution stops early after reaching the end point.
Because the end point ends at a power transformer, which is a building type, the paths ends at in a \textit{Prohibited} Area.
Therefore, areas even farther away from the starting point have been explored first.

### 2023-03-04 paper/paper-CableRoute.tex
added Supplement S1
Related works
Examine solutions

\newacronym{wfs}{wfs}{Web Feature Service}
\newacronym{wps}{wps}{Web Processing Service}
\newacronym{res}{res}{resolution}
\newacronym{r}{r}{ratio}
\newacronym{al}{al}{all touched}
\newacronym{t}{t}{True}
\newacronym{f}{f}{False}
\newacronym{agg.}{agg.}{aggregated}
\newacronym{rel}{rel}{relative}
\newacronym{corr}{corr}{corrected}

@@

	\begin{abstract}
		add as final part
	\end{abstract}

	%%
	%% The code below is generated by the tool at https://dl.acm.org/ccs.cfm.
	%% Please copy and paste the code instead of the example below.
	%%
	\begin{CCSXML}
		<ccs2012>
		<concept>
		<concept_id>10010520.10010553.10010562</concept_id>
		<concept_desc>Computer systems organization~Embedded systems</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10010520.10010575.10010755</concept_id>
		<concept_desc>Computer systems organization~Redundancy</concept_desc>
		<concept_significance>300</concept_significance>
		</concept>
		<concept>
		<concept_id>10010520.10010553.10010554</concept_id>
		<concept_desc>Computer systems organization~Robotics</concept_desc>
		<concept_significance>100</concept_significance>
		</concept>
		<concept>
		<concept_id>10003033.10003083.10003095</concept_id>
		<concept_desc>Networks~Network reliability</concept_desc>
		<concept_significance>100</concept_significance>
		</concept>
		</ccs2012>
	\end{CCSXML}

	\ccsdesc[500]{Computer systems organization~Embedded systems}
	\ccsdesc[300]{Computer systems organization~Redundancy}
	\ccsdesc{Computer systems organization~Robotics}
	\ccsdesc[100]{Networks~Network reliability}

	%%
	%% Keywords. The author(s) should pick words that accurately describe
	%% the work being presented. Separate the keywords with commas.
	\keywords{datasets, neural networks, gaze detection, text tagging}

@@

	Sometimes, finding the shortest path is not sufficient.
	Additional parameters also have to be taken into consideration.
	As the steepness of a road or the soil, play an important role for the building cost of a road or pipeline
	\cite{suleiman_optimal_2015}.
	For planing the additional routes for a power grid, additional aspects as legal regulations and acceptance
	by the local population have to be taken in consideration.
	Also technical aspects, as the effects on the grid stability might be further points to consider.\cite{schafer_understanding_2022}

	Due to the increasing need for renewable energy wind off shore wind turbines are source which currently supplies 5.5~\% annual percentage in 2020 of the German energy mix.~\cite{noauthor_nettostromerzeugung_2021}
	For wind energy in general highest efficiency can only be archived with high wind speeds. Highest wind speeds are reached along the cost lines in the north of Germany.
	In contrast, most consumers, as industry are situated in south Germany.
	Source and consumer have to be linked via new power lines.

	Other methods as the multi-criteria decision analysis take further aspects and stakeholder as experts, public and decision maker and into consideration.\cite{bertsch_participatory_2016}

@@

	\section{Methods}\label{sec:methods}

	\input{methods}

	\section{Results}\label{sec:results}

	\input{results}

@@

	\section{Related Works}\label{sec:related-works}

	\section{Conclusion}\label{sec:conclusion}
	When using the researched strategies, the on medium resolution raster, the computation for high resolution results might successfully be reduced, without compromising the run time for worse distances to the least cost path from the high resolution raster.
	\todo{Befragung: local population, relative weights per district?}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{Web_Processing.bib}

>>>>

\newacronym{wfs}{wfs}{Web Feature Service}
\newacronym{wps}{wps}{Web Processing Service}
\newacronym{res}{res}{resolution}
\newacronym{r}{r}{ratio}
\newacronym{al}{al}{all touched}
\newacronym{t}{t}{True}
\newacronym{f}{f}{False}
\newacronym{agg.}{agg.}{aggregated}
\newacronym{rel}{rel}{relative}
\newacronym{corr}{corr}{corrected}
\newacronym{MCDA}{MCDA}{multi-criteria decision analysis}

@@

	\begin{abstract}
		The least cost paths for a power line route from a power station near the German shore line is computed to a power station further inland.
		Down sampling and clipping studied for a speed-up of the computation.
		The path from clipped cost raster often matches the original path.
		The speed-up of the clipping can not be known before hand.
	\end{abstract}

	%%
	%% The code below is generated by the tool at https://dl.acm.org/ccs.cfm.
	%% Please copy and paste the code instead of the example below.
	%%
	\begin{CCSXML}
		<ccs2012>
		<concept>
		<concept_id>10010147.10010341</concept_id>
		<concept_desc>Computing methodologies~Modeling and simulation</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10002944.10011123.10011133</concept_id>
		<concept_desc>General and reference~Estimation</concept_desc>
		<concept_significance>100</concept_significance>
		</concept>
		</ccs2012>
	\end{CCSXML}

	\ccsdesc[500]{Computing methodologies~Modeling and simulation}
	\ccsdesc[100]{General and reference~Estimation}

	%%
	%% Keywords. The author(s) should pick words that accurately describe
	%% the work being presented. Separate the keywords with commas.
	\keywords{GIS, least cost path}

@@

	Sometimes, finding the shortest path is not sufficient.
	Additional parameters also have to be taken into consideration.
	As the steepness of a road or the soil, play an important role for the building cost of a road or pipeline
	\cite{suleiman_optimal_2015}.
	For planing the additional routes for a power grid, additional aspects as legal regulations and acceptance
	by the local population have to be taken in consideration.
	Also technical aspects, as the effects on the grid stability might be further points to consider~\cite{schafer_understanding_2022}.

	Due to the increasing need for renewable energy wind off shore wind turbines are source which currently supplies 5.5~\% annual percentage in 2020 of the German energy mix~\cite{noauthor_nettostromerzeugung_2021}
.	For wind energy in general highest efficiency can only be archived with high wind speeds.
	Highest wind speeds are reached along the cost lines in the north of Germany.
	In contrast, most consumers, as industry are situated in south Germany.
	Source and consumer have to be linked via new power lines.

	Other methods as the multi-criteria decision analysis take further aspects and stakeholder as experts, public and decision maker and into consideration~\cite{bertsch_participatory_2016}.

@@

	\section{Methods}\label{sec:methods}
	\input{methods}

	\section{Results}\label{sec:results}
	\input{results}

@@

	\section{Related Works}\label{sec:related-works}
	In contrast to GIS analysis, further effort can be done with a \acrfull{MCDA}\todo{Pohekar and Ramachandran 2004, Wang 2009, Riberio 2011}.
	The uncertainties connected with \acrshort{MCDA} are data uncertainties, preferential uncertainties and model uncertainties.
	These uncertainties are examined by a with a sensitivity analysis \todo{Eßer-Frey} or simulation~\cite{butler_simulation_1997}.

	The different models of the power market models span from not modeling the grid at all to models that includes Kirchhoffs laws.
	However, the actual planning of power grids is computational complex and the actual grid data are confidential~\cite{bertsch_participatory_2016}.
	Some models include not only the grid of a nation alone~\cite{dietrich_will_2010}, but models do not include both model the expansion planing for a longer time period and the effect of power transition~\cite{bertsch_participatory_2016}.
	But economic modeling is not sufficient for planning modern routes, as the aspect of environmental sustainability, security of supply and the public acceptance play an important role~\cite{hauff_gesellschaftliche_2011}.

	\section{Conclusion}\label{sec:conclusion}
	When using the researched strategies, the on medium resolution raster, the computation for high resolution results might successfully be reduced, without compromising the run time for worse distances to the least cost path from the high resolution raster.
	\todo{survey: local population, relative weights per district?}

@@

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
%%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{unsrt}
\bibliography{Web_Processing.bib}

### 2023-03-04 paper/results.tex
added Supplement S1
Related works
Examine solutions

The zonal stat (see table~\ref{tab:3}) for a buffer of 100 m (5 m) around the path has been used, to estimate the
percentage of which costs levels are around the path.
When using all\_touched True rasterization with higher resolution the tendency is to use a higher percentage of the
Preferential Level and less the NoRestriction Level.\todo{Interpretation:}
The ratio of the 100 m buffered least cost path, strongly shifted  to Levels lower costs.

@@

\subsubsection{Check solution for least cost path between different points}

>>>>

The zonal stat (see table~\ref{tab:3}) for a buffer of 100 m (5 m) around the path has been used, to estimate the
percentage of which costs levels are around the path.
When using all\_touched True rasterization with higher resolution the tendency is to use a higher percentage of the
\textit{Preferential Level} and less the\textit{NoRestriction} Level.\todo{Interpretation:}
The ratio of the 100 m buffered least cost path, strongly shifted  to Levels lower costs.

@@

\subsubsection{Examine the proposed solutions}
To broaden the view and verify the current result, four different routes should be found with the presented strategies applied.
Two paths form the starting point to two new points in the south east of the investigated area and two paths from the north, north east of the investigates area to the ending point.

For three of the four routes the least cost path computation from the clipped raster, was able to compute the expected result.
For the forth path, the
least cost path from the 5~m resolution raster was out side of the buffer around the least cost path from the 50~m resolution raster.
The speed up from the clipping of the higher resolution raster depends on the amount of pixels that, have been clipped. 
Bi-linear down sampling the of the high resolution raster to a medium resolution, did not result in any benefits compared to an original medium resolution raster.
The resolution corrected aggregated costs of the least cost path from the down sampled raster are higher, than those, from the higher 5~m resolution raster and the medium 10~m resolution raster.
In addition, is the distance, from this path to the path from the high resolution raster much higher, than the distance of path from the original 10~m resolution raster to the path from the 5~m resolution raster (see table~\ref{tab:6}).
\todo{interpretation Why, down sampling so different???}

\begin{table}[h!]
	\caption{Length of the path, the resolution corrected costs and the mean distance to the path created from the 5~m resolution all touched false raster for the four control routes, for the reference path of constructed from the 5~m  and 10~m raster and the down 5~m to 10~m down sampled raster and the 5~m clipped raster.}
	\label{tab:6}
	\centering
	\begin{tabular}{ r  r  r  r  r}
		Route & Method & $length /m$ & $costs_{al=f}$ & $d_{mean}$ /m \\
		\hline
		P1-E & 5~m 			& 107889.58 & 208547.79 &        \\
		 	 & Clipped 		& 107889.58 & 208547.79 &   0.0  \\
		 	 & Down			&  96754.20 & 212910.95 & 628.05 \\
		 	 & 10~m 		& 107232.94 & 203010.15 & 103.49 \\
		\hline
		P2-E & 5~m 			& 103706.41 & 155567.86 &        \\
		 	 & Clipped 		& 103706.41 & 155567.86 &   0.00 \\
		 	 & Down 	    &  92403.29 & 158238.58	& 639.88 \\
		 	 & 10~m 		& 104249.94 & 149899.72 & 177.68 \\
		\hline
		S-P3 & 5~m 			& 102187.09 & 34503.81 	&         \\
			 & Clipped 		&  90377.39 & 37926.14 	& 4465.37 \\
			 & Down 	    &  94125.55 & 37574.93 	&  742.41 \\
			 & 10~m 		& 102461.58 & 32445.96 	&   81.18 \\
		\hline
		S-P4 & 5~m 			& 96449.22 	& 33865.53 	&  		\\
		 	 & Clipped 		& 96449.22 	& 33865.53 	& 0.00 	\\
			 & Down 		& 87861.12 	& 36462.72 	& 796.40\\
			 & 10~m 		& 96739.47 	& 31899.31	& 83.46 \\
